### 2018-07-30 manuscript.rmd
rerun diet associations and OUwie w/ new phylo

#PhyloPCA on means
PPCA_raw = phyl.pca(raw_tree, raw_matrix)
PPCA_compound = phyl.pca(compound_tree, compound_matrix)
PPCA %>% biplot(main=paste(signif(summary(PPCA)$importance[2,1]*100,3),"%"), ylab=paste(signif(summary(PPCA)$importance[2,2]*100,3),"%"), cex = .6, expand =1)

@@

```{r diet_regime_tree}
regimetree = dprunedTree
hypdiet = c("Mixed", "Mixed", "Crustacean", "Copepod", "Mixed", "Crustacean", "Crustacean", "Ostracod", "Fish", "Fish", "Crustacean", "Mixed", "Mixed", "Copepod")
names(hypdiet) = regimetree$tip.label
DietAnc = ace(hypdiet, regimetree, type = "discrete")$lik.anc
HypDietAnc = 1:nrow(DietAnc)
for(row in 1:nrow(DietAnc)){
  SCR = scale(DietAnc[row,])
  print(SCR)
  HypDietAnc[row] <- rownames(SCR)[which(SCR[,1] == max(SCR[,1]))] %>% print()
}
regimetree$node.label = as.factor(HypDietAnc)
plotTree(regimetree)
nodelabels(text=regimetree$node.label,frame="none",adj=c(1.6,-0.45), cex=0.6);tiplabels(text=hypdiet, frame="none", cex=0.6, adj=c(0,2))
```

>>>>

#PhyloPCA on means
PPCA_raw = phyl.pca(raw_tree, raw_matrix)
PPCA_compound = phyl.pca(compound_tree, compound_matrix)
PPCA_raw %>% biplot(main=paste(signif(summary(PPCA_raw)$importance[2,1]*100,3),"%"), ylab=paste(signif(summary(PPCA_raw)$importance[2,2]*100,3),"%"), cex = .6, expand =1)
PPCA_compound %>% biplot(main=paste(signif(summary(PPCA_compound)$importance[2,1]*100,3),"%"), ylab=paste(signif(summary(PPCA_compound)$importance[2,2]*100,3),"%"), cex = .6, expand =0.4)

@@

```{r diet_regime_tree}
regimetree = dprunedTree
hypdiet = c("Mixed", "Mixed", "Crustacean", "Copepod", "Mixed",  "Fish", "Fish", "Ostracod", "Copepod", "Copepod", "Mixed", "Copepod")
names(hypdiet) = regimetree$tip.label
DietAnc = ace(hypdiet, regimetree, type = "discrete")$lik.anc
HypDietAnc = 1:nrow(DietAnc)
for(row in 1:nrow(DietAnc)){
  SCR = scale(DietAnc[row,])
  print(SCR)
  HypDietAnc[row] <- rownames(SCR)[which(SCR[,1] == max(SCR[,1]))] %>% print()
}
regimetree$node.label = as.factor(HypDietAnc)
plotTree(regimetree)
nodelabels(text=regimetree$node.label,frame="none",adj=c(1.6,-0.45), cex=0.6);tiplabels(text=hypdiet, frame="none", cex=0.6, adj=c(0,2))
```
